---
title: "Homework1.1"
author: "Lindsay Rutter"
date: "7/17/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r readData}
library(stats)
library(broom)
library(readr)
library(dplyr)
library(ggplot2)

dat <- read_csv("../priemelDataReconstruction.csv")
dat <- as.data.frame(dat)
colnames(dat) <- c("serum", "ovbv")
```

```{r plotOVBV}
dat %>% ggplot(aes(x=serum, y=ovbv)) + geom_point()
```

As the serum level increases, the OB/BV values decrease. However, there are very low OB/BV values for low serum levels as well.

Next, I fit a logisitic regression to determine the probability that requirements are met (OV/BV is 2 or less) as a function of serum level.

```{r logRegression}
glm(ovbv~serum, data=dat)
```

After that, I restrict the set of patients to exclude those with serum values far from the target level (e.g., 10 nmol/L or less), and reanalyze.

```{r logRegressionLess10}
dat10 <- dat %>% filter(serum<10)
results <- glm(ovbv~serum, data=dat10)
```

This model gives us an intercept of `r tidy(results)$estimate[1]` and a slope of `r tidy(results)$estimate[2]`.
